Volatility and the Buyback Anomaly: Interactive Tool

### 2017-02-17 manuscript.Rnw
compiles all the way

So far all our events are equally weighted. \cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly. However, as pointed out by \cite{LoughranRitter2000}, small firms are more likely to be mispriced as they are less followed by analysts. Hence managers of small firms are better able to take advantage of mispricing than managers of large firms, which is the reason why firm size is one of the components of the U-index. So value weighting the events would simply bias the results toward zero. And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events. So the buyback anomaly is not economically important and does not challenge the basic premise that ???the market??? represented by a value-weighted index is priced correctly. Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant, especially for the high U-index firms. These firms had a market capitalization less than \$2,971 million in 2015. The fact that the buyback anomaly is a small cap anomaly makes it more likely that excess returns are evidence that managers (at least in these firms) time the market based on their information advantage relative to investors.  It may also explain why the anomaly persists as the capacity of small cap funds (and therefore management fees) is smaller than the capacity of large cap funds.

@@

\bibliographystyle{jf}
\bibliography{BibliographyInitname}

>>>>

So far all our events are equally weighted. \cite{MitchellStafford2000} argue that events should be value weighted to test whether they represent an economically important anomaly. However, as pointed out by \cite{LoughranRitter2000}, small firms are more likely to be mispriced as they are less followed by analysts. Hence managers of small firms are better able to take advantage of mispricing than managers of large firms, which is the reason why firm size is one of the components of the U-index. So value weighting the events would simply bias the results toward zero. And indeed, when we value-weight the events (see Table \ref{tbl:valuetable} Panel A) long-term excess returns become statistically insignificantly different from zero when using the total sample of events. So the buyback anomaly is not economically important and does not challenge the basic premise that the market represented by a value-weighted index is priced correctly. Note, however, if we eliminate the firms with are in the top $25^{th}$ market capitalization percentile (see Table \ref{tbl:valuetable}, Panel~B) the results become again significant, especially for the high U-index firms. These firms had a market capitalization less than \$2,971 million in 2015. The fact that the buyback anomaly is a small cap anomaly makes it more likely that excess returns are evidence that managers (at least in these firms) time the market based on their information advantage relative to investors.  It may also explain why the anomaly persists as the capacity of small cap funds (and therefore management fees) is smaller than the capacity of large cap funds.

@@

\bibliographystyle{jf}
\bibliography{Bibliography}
